### 2022-04-20 response_reviewers.tex

5. In Rule 4, vis a vis bias, bias against people with disability and ethnic minorities should also be highlighted.

\begin{Reply}

    We had mentioned [perceived] ethnicity as one of the aspects of diversity that may be inferred (correctly or incorrectly) via written communication and be a source of unconscious bias  (line \ref{bias}, \textit{`their perceived origin, ethnicity, gender, or native language'}).

    Conscious and unconscious bias can also operate when the submitted work is not written, but rather in video form. We added a short mention and citation about how video abstracts can be exclusionary (Spitschan et al 2021) by adding barriers to people with visible disabilities, diverse body types, non-native language speakers, or less resources to create videos (lines \ref{video-1} to \ref{video-2}).

    Spitschan M, Yehudi Y, Acion L. Video Grant Proposals Could Be Exclusionary. 
    Nature. 2021; 592(7852):26–26. doi:10.1038/d41586-021-00862-x.

    We thank the reviewer for this comment that led us to the current addition.
\end{Reply}

@@

6. In Rule 8, inclusive communication strategy - it is important that the speakers from diverse backgrounds, especially from ethnic minorities etc are highlighted or given prominence in social media strategy or communication. Often, these speakers face relatively less focus. This may be discussed.

\begin{Reply}

    We added the following text to the manuscript (lines \ref{promotion-1} to \ref{promotion-2}) to address this comment: 
    \textit{During the conference, pay special attention to promoting the sessions led, chaired, and presented by people in minoritized groups, multilingual sessions, and the diversified thematic sessions (see \textbf{Rule 4}) to give them the same visibility as all other sessions.}
\end{Reply}

@@

7. In Conclusion, suggest also adding that issues of diversity and inclusion have come to fore even more during COVID-19 as we witness exacerbation of inequities disadvantaging those from vulnerable backgrounds (see https://pubmed.ncbi.nlm.nih.gov/33343410/PMID: 33343410)

\begin{Reply}

    We appreciate the suggestion and agree that the COVID-19 pandemic contributed to the exacerbation of inequity. 
    We would like our manuscript to help inspire and guide the organization of more inclusive conferences across the world, well beyond the pandemic. To ensure this broad applicability, we minimized mentions of the pandemic to only when deemed necessary: to give context to the conference we organized, and to talk about virtual conference formats that prevailed during the last two years.

    Once again, we thank all the reviewers for their comments and careful consideration.  The feedback has helped clarify the language and the message.
\end{Reply}
